\documentclass[a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{palatino}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listingsutf8}
\usepackage{listings}
\usepackage{color}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{mathpartir}
\usepackage{cleveref}
\usepackage{xspace}

\usepackage[most]{tcolorbox}
\usepackage{environ}
\usepackage{changepage}   % for the adjustwidth environment
\usepackage[thmmarks]{ntheorem}
\usepackage{minted}

% SOLUTION
\newtcolorbox{solution}[1][]{
    colback=gray!10,
    colframe=gray!50,
    coltitle=black,
    sharp corners,
    breakable,
    enhanced,
    #1
}

% COLOURS
\definecolor{blue}{RGB}{8,71,150}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{orange}{rgb}{1.0,0.55,0}

\title{
    \color{mauve}Artificial Intelligence in Games\\[1ex]
    Project - NEAT Application to the Racing Cars Game\\[1ex]
}
\author{
    Mestrado em Engenharia Informática\\
    Faculdade de Ciências da Universidade de Lisboa\\ \\
    Group 05\\ \\
    Bruno Faustino fc59784\\
    Rodrigo Neto fc59850
}
\date{2025/2026}

\begin{document}
\maketitle
\raggedright
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

A very good introduction!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Controller Inputs %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Controller Inputs}
\label{sec:controller-inputs}

Remarkable controller inputs!

%-------------------------------- Waypoints Car Inputs ------------------------------%
\subsection{Waypoints Car Inputs}
\label{subsec:waypoints-car-inputs}

Right on point!

%--------------------------------- Radars Car Inputs --------------------------------%
\subsection{Radars Car Inputs}
\label{subsec:radars-car-inputs}

It's off the Radar!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Radars %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radars}
\label{sec:radars}

Very well placed radars!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Analysis %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
\label{sec:analysis}

Very informative analysis!

%%%%%%%%%%%%%%%---------------- Waypoints Car Analysis ----------------%%%%%%%%%%%%%%%
\subsection{Waypoints Car Analysis}
\label{subsec:waypoints-car-analysis}

Analysis right on point!

%------------------------------------ Experiments -----------------------------------%
\subsubsection{Experiments}
\label{subsubsec:waypoints-experiments}

So much experience!

%------------------------------------ Parameters ------------------------------------%
\subsubsection{Parameters}
\label{subsubsec:waypoints-parameters}

Very well-chosen parameters!

%------------------------------- Controller Performance -----------------------------%
\subsubsection{Controller Performance}
\label{subsubsec:waypoints-controller-performance}

Very controlled performance indeed!

%%%%%%%%%%%%%%%------------------ Radars Car Analysis -----------------%%%%%%%%%%%%%%%
\subsection{Radars Car Analysis}
\label{subsec:radars-car-analysis}

Analysis is off the radar!

%------------------------------------ Experiments -----------------------------------%
\subsubsection{Experiments}
\label{subsubsec:radars-experiments}

So much experience!

%------------------------------------ Parameters ------------------------------------%
\subsubsection{Parameters}
\label{subsubsec:radars-parameters}

Very well-chosen parameters!

%------------------------------- Controller Performance -----------------------------%
\subsubsection{Controller Performance}
\label{subsubsec:radars-controller-performance}

Very controlled performance indeed!

%%%%%%%%%%%%%%%------------ Performance Comparison of the Cars --------%%%%%%%%%%%%%%%
\subsection{Performance Comparison of the Cars}
\label{subsec:performance-comparison}

What a performance!

\end{document}
